The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Added Zelig chart

## From Education to Entrepreneurship

*Text from Thierry*

@@

We decided to ignore country-specific effects because the change in the intercept resulting from fixed effects was small and the slope of the fixed effects and OLS models are very similar.

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 20:70)

@@

```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Plot simulation
plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
```

## New
```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

@@

>>>>

## Research Interest

**What determines entrepreneurship?**

- Economic and structural factors: Already searched

- Educational and cultural factors: Hardly searched

- Even when focused on attitudes / Entrepreneurship, studies look more at what attitudes are favourable, almost none searched what determines these attitudes.

## Causal Chain

1. Education System that reinforces Self-confidence

2. Higher degree of individual self-esteem

3. Higher probability an individual becomes an entrepreneur

4. Higher rate of entrepreneurship at a country-level

## Where our Intuition Came From

Variable | France | UK
-------------|---------------|---------
Fear of Failure (GEM 2012) | 43% | 36%
Perceived Capabilities (GEM 2012) | 36% | 47%
Sense of belonging (PISA 2012) | 47% | 79%

## What is PISA

- PISA: "Programme for International Student Assessment is a triennial international survey which aims to evaluate education systems worldwide by testing the skills and knowledge of 15 year old students."

- Data availability prevented us from using PISA data for this project. For instance, for 2015 PISA will be looking at science education.

## What is GEM

- The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.

- Only 10 countries at first, now covering 75% of world population and 89% of world GDP

- GEM is being used is regularly refered to in research, including in OECD reports.

- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.

- NES or National Expert Survey looks at 9 entrepreneurial framework conditions (4 national experts for each)

## Estimation Strategy

Variable | Indicator 
-------------|---------------
Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

## Explaining Way of Teaching

- In the absence of an  indicator directly aligned with our research design, we turned to an item of the GEM NES survey as a proxy, question D01:

- "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"

- But there is a clear lack of consistency in the data.

- Many flaws : scale, methodology for collection (poor time management, personal connections)

## Perceived Capabilities

- "Percentage of 18-64 population who believe they have the required skills and knowledge to start a business"

- This figure is a national-level precentage

- This measure was chosen to provide some insight on how personal values are shaped, especially in terms of self-confidence.

## Differences in Perceived Capability in OECD Countries

# Import GEM data frame
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
PC1 <- countrycode(PerceivedCapabilities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedCapabilities$new.col <- PC1

# Reorder columns so country code is first
PC2 <- PerceivedCapabilities[,c(15,1:14)]

# Rename first column
PC3 <- plyr::rename(x = PC2, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(PC3) <- gsub("X", "", names(PC3))

# Set columns as numeric
PC3[,"2001"] <- as.numeric(PC3[,"2001"])
PC3[,"2002"] <- as.numeric(PC3[,"2002"])
PC3[,"2003"] <- as.numeric(PC3[,"2003"])
PC3[,"2004"] <- as.numeric(PC3[,"2004"])
PC3[,"2005"] <- as.numeric(PC3[,"2005"])
PC3[,"2006"] <- as.numeric(PC3[,"2006"])
PC3[,"2007"] <- as.numeric(PC3[,"2007"])
PC3[,"2008"] <- as.numeric(PC3[,"2008"])
PC3[,"2009"] <- as.numeric(PC3[,"2009"])
PC3[,"2010"] <- as.numeric(PC3[,"2010"])
PC3[,"2011"] <- as.numeric(PC3[,"2011"])
PC3[,"2012"] <- as.numeric(PC3[,"2012"])
PC3[,"2013"] <- as.numeric(PC3[,"2013"])

# Save cleaned df
PC4 <- PC3

# Generate a new column with mean of all other columns
PC3$mean <- rowMeans(subset(PC3, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007",
                                            "2008", "2009", "2010", "2011", "2012", "2013")),
                     na.rm = TRUE)

# Drop year columns, leaving only mean column
PC3$'2001' <- NULL
PC3$'2002' <- NULL
PC3$'2003' <- NULL
PC3$'2004' <- NULL
PC3$'2005' <- NULL
PC3$'2006' <- NULL
PC3$'2007' <- NULL
PC3$'2008' <- NULL
PC3$'2009' <- NULL
PC3$'2010' <- NULL
PC3$'2011' <- NULL
PC3$'2012' <- NULL
PC3$'2013' <- NULL

# Create 
PC3[, 3] <- round(log(PC3[, 3]), digits = 2)
```

# Plot perceived capabilities map
PC_map <- gvisGeoChart(PC3, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate F4 (perceived capabilities) df
#DroppedPC4 <- PC4

# Drop iso2c in Dropped4
#DroppedF4$iso2c <- NULL

# Print the map
print(PC_map, tag = 'chart')

## Time Variation in Perceived Capabilities
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

# Subset Opp2
PC5 <- subset(PC4, iso2c %in% myvars2)

# Melt Opp2 df
PC6 <- melt(data = PC5,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(PC6) <- gsub("value", "PerceivedCapabilities", names(PC6))
names(PC6) <- gsub("variable", "Year", names(PC6))

PC6$iso2c <- NULL
```

# Create plot
ggplot(PC6,aes(x = Year, y = PerceivedCapabilities, colour = Country, group = Country)) + geom_line()

## Fear of Failure

- "Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."

## Perceived Opportunities

- "Percentage of 18-64 population who see good opportunities to start a firm in the area where they live"

- Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.

@@

- Our regression equations were run both with and without considering country-specific effects.  For the purposes of illustrating our results, we have chosen to ignore the country-specific effects.

- We decided to do this because the coefficients do not change signficantly when the country-specific effects are ignored.

## Results: PercentIntention as a Dependent Variable

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, WayofTeaching = 1.53:3.278)

@@

```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Plot simulation
plot(simz2, xlab = 'WayofTeaching', ylab = 'PercentIntention | WayofTeaching')
```

## Results: PercentIntention as a Dependent Variable

```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

library(Zelig)

# Run a RE regression
Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")

# Set range of PercentPerceived values in simulation
x.out3 <- setx(Z1, PercentPerceived = 9:67)

# Run simulation (default 1000 trials)
simz3 <- sim(Z1, x = x.out3)

@@

```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Plot simulation
plot(simz3, xlab = 'PercentCapabilities', ylab = 'PercentIntention | PercentCapabilities')
```

```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
